---
title: "Developing Data Products Final Project"
author: "Reza Zahedi"
date: "November 6, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Discription
<br><br><center>
This app is designed to draw an n-edged shape, and color it usig the Red, Green and Blue components of a user specified color. It olso returns the hexadecimal color equivalent to the color selection.
<br><br>

You can find the app <br>[HERE](https://bleedereagle.shinyapps.io/Circle/)
</center>

## Inputs and Outputs

#### Inputs:
- Number of edges
- Red, green and blue intesity, from 0 to 255
- X and Y axis limits, to change something :D

#### Outputs:
- The hexadecimal color equvalent
- The plot, as depicted in the next slide

## Sample Plot Output

```{r, fig.height= 4}
cx = 10
cy = 10
rad <- 5
n <- 6
red = 85; green = 206; blue = 185;
ylim = c(5, 15); xlim = c(0, 20);
lineWidth <- 7

theta <- seq(from = pi/n , to = 2 * pi + pi/n, length.out = n+1)

x <- cx + rad * cos(theta)
y <- cy + rad * sin(theta)

plot(x, y, ylim = ylim, xlim = xlim, type = "l", bty = "n",
     col = rgb(red, green, blue, max=255), lwd = lineWidth)
points(10, 10, pch = 19)
```

- number of edges = `r n`
- red = `r red`, green = `r green`, blue = `r blue`  
- hexadecimal color is: `r rgb(red, green, blue, maxColorValue = 255)`